The imprint of global magma oceans on exoplanet demographics

### 2022-12-08 src/tex/ms.tex
remove synthetic population scatter plot
will be combined with hypothesis plot
Unify MO/no MO and hypotheses plots, describe in text

Figure~\ref{fig:radiuscomparison} shows the different mass-radius relations of the three cases for a fiducial water mass fraction of $x_{H_2O}= \wrr$.
In general, steam atmospheres (case B) cause a significant radius increase, which is slightly reduced when water incorporation in the melt is allowed (case C).

\begin{figure}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/synthetic_population.pdf}
        \caption{Total synthetic planet population and transiting planets.}
        \label{fig:synthetic_population}
    \end{centering}
\end{figure}

\begin{figure*}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/has_magmaocean.pdf}
        \caption{Synthetic planets with and without magmaoceans as a function of Solar-equivalent semi-major axis}
        \label{fig:has_magmaocean}
    \end{centering}
\end{figure*}

@@

\begin{figure}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/HnullHmo.pdf}
        \caption{Average radius predictions of the null hypothesis and magma ocean hypothesis. The sharp boundary of the runaway greenhouse regime causes a discontinuity at the threshold instellation $S_\mathrm{thresh}$, which we set to \SI{280}{\watt\per\meter\squared} in the fiducial case.}
        \label{fig:HnullHmo}
    \end{centering}
\end{figure}
    Figure~\ref{fig:HnullHmo} shows the null and alternative hypotheses as a function of instellation.
    The value for the average radius \textit{outside} the runaway greenhouse regime was computed from our nominal observed sample, whereas the radius change in the magma ocean case compared to the null hypothesis is a prediction from the magma ocean model, evaluated on the same sample.

>>>>

Figure~\ref{fig:radiuscomparison} shows the different mass-radius relations of the three cases for a fiducial water mass fraction of $x_{H_2O}= \wrr$.
In general, steam atmospheres (case~B) cause a significant radius increase, which is slightly reduced when water incorporation in the melt is allowed (case~C).
Our nominal simulation setup is such that all planets receiving an instellation $S < S_\mathrm{thresh}$ follow relation~A, and all planets with $S > S_\mathrm{thresh}$ follow relation~C.

@@

\begin{figure}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/HnullHmo.pdf}
        \caption{Planets above and below the runaway greenhouse threshold.
        \textit{Top}: Planet state as a function of orbital period. Planets with and without a runaway greenhouse climate mix and are not distinguishable in period space.
        \textit{Bottom}: Radii of synthetic planets with injected radius deviation as a function of instellation. Only the planets marked as transiting are observable. Above the runaway greenhouse threshold $S_\mathrm{thresh} =\SI{280}{\watt\per\meter\squared} $, radii are inflated by the amount indicated with gray lines. The sharp boundary at $S_\mathrm{thresh}$ causes a discontinuity in the average planet radius (blue). This magma ocean hypothesis can be tested agains the null hypothesis $H_0$ (green), where average radii are independent of instellation.}
        \label{fig:HnullHmo}
    \end{centering}
\end{figure}
    Figure~\ref{fig:HnullHmo} shows the null and alternative hypotheses as a function of instellation.
    The value for the average radius \textit{outside} the runaway greenhouse regime was computed from our nominal observed sample, whereas the radius change in the magma ocean case compared to the null hypothesis is a prediction from the magma ocean model, evaluated on the same sample.
